Effect of character correlation

### 2018-04-19 Analysis/02-EffectCorrelationFullResults.Rmd
Uploaded analysis

```{r, echo = FALSE}
library(knitr)
## Setting the table captions
captions_pooled_scenarios <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled scenarios.")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
library(xtable)
make.xtable(scenarios, caption = captions_pooled_scenarios, label = "Full_Tab_pooledscenarios", path = "../Writing/Tables/")
```

@@

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Full_Tab_signif", path = "../Writing/Tables/")
```

@@

```{r, warning = FALSE}
## Summarise into a table
scenario_list <- list(scenario_RF_norm, scenario_Tr_norm, scenario_RF_null, scenario_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(scenario_list, comp.label = comp.labels, metric.label = metric.labels)
```

```{r, echo = FALSE}
## Caption
cap_pool_scen_test <- paste("Difference between the pooled scenarios. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(test_table, caption = cap_pool_scen_test, label = "Full_Tab_pooledscenarios_test", path = "../Writing/Tables/")
```

@@

```{r, warning = FALSE}
## Pooling the data per character
character_RF_norm <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "RF", best = "norm")
character_Tr_norm <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "Tr", best = "norm")
character_RF_null <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "RF", best = "rand")
character_Tr_null <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "Tr", best = "rand")

@@

```{r, echo = FALSE}
## Setting the table captions
captions_pooled_characters <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled number of characters.")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(characters, caption = captions_pooled_characters, label = "Full_Tab_pooledcharacters", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Full_Tab_signif")
```

@@

```{r, echo = FALSE}
## Caption
cap_pool_char_test <- paste("Difference between the pooled number of characters. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(test_table, caption = cap_pool_char_test, label = "Full_Tab_pooledscharacters_test", path = "../Writing/Tables/")
```

@@

```{r, echo = FALSE}
## Setting the table captions
captions_pooled_taxa <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled number of taxa.")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(taxa, caption = captions_pooled_taxa, label = "Full_Tab_pooledtaxa", path = "../Writing/Tables/")
```

@@

```{r, echo = FALSE}
## Caption
cap_pool_tax_test <- paste("Difference between the pooled number of taxa. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(test_table, caption = cap_pool_tax_test, label = "Full_Tab_pooledstaxa_test", path = "../Writing/Tables/")
```

@@

```{r, echo = FALSE}
## Setting the table captions
captions_pooled_methods <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled methods.")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(methods, caption = captions_pooled_methods, label = "Full_Tab_pooledmethod", path = "../Writing/Tables/")
```

@@

```{r, warning = FALSE}
## Summarise into a table
methods_list <- list(method_RF_norm, method_Tr_norm, method_RF_null, method_Tr_null)
comp.labels <- c("Best", rep("", 3), "Null", rep("", 3))
metric.labels <- rep(c("RF", "", "Tr", ""), 2)
test_table <- pair.test.table(methods_list, comp.label = comp.labels, metric.label = metric.labels)
```

```{r, echo = FALSE}
## Caption
cap_pool_met_test <- paste("Difference between the pooled methods. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide'}
make.xtable(test_table, caption = cap_pool_met_test, label = "Full_Tab_pooledsmethods_test", path = "../Writing/Tables/")
```

@@

```{r}
## Summarising the data
sum_RF_best <- apply.test(whole_data, "RF", "norm", NULL)
sum_Tr_best <- apply.test(whole_data, "Triples", "norm", NULL)
sum_RF_null <- apply.test(whole_data, "RF", "null", NULL)
sum_Tr_null <- apply.test(whole_data, "Triples", "null", NULL)
```

```{r, echo = FALSE}
## Setting the table captions
captions_summary <- paste("Summary statistics of the normalised", rep(c("Robinson-Fould", "Triplets"), 2), "distance to the", c(rep("best", 2), rep("null", 2)), "tree.")

@@

```{r, echo = FALSE, eval = TRUE, print = FALSE, result = 'hide'}
## Labels
labels_summary <- paste0("Full_Tab_Summary", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

@@

```{r}
## Applying an lm to all the data with error
results <- test.effect.aov(whole_data,
  formula = NTS ~ scenario + (1|method) + (1|taxa) + (1|character), fun = lmer)
```

@@

```{r}
## Running the pairwise Bhattacharrya Coefficient analysis:
bc_RF_best <- apply.test(whole_data, "RF", "norm", bhatt.coeff)
bc_Tr_best <- apply.test(whole_data, "Triples", "norm", bhatt.coeff)
bc_RF_null <- apply.test(whole_data, "RF", "null", bhatt.coeff)
bc_Tr_null <- apply.test(whole_data, "Triples", "null", bhatt.coeff)
```

```{r, echo = FALSE}
## Tables
kable(bc_RF_best, row.names = FALSE, digit = 3)
kable(bc_RF_best, row.names = FALSE, digit = 3)
kable(bc_RF_best, row.names = FALSE, digit = 3)
kable(bc_RF_best, row.names = FALSE, digit = 3)
```

```{r, echo = FALSE}
## Setting the table captions
captions_bc <- paste0("Bhattacharrya Coefficient (",rep(c("Robinson-Fould distance", "Triplets distance"), 2) ," from the ",c(rep("best", 2), rep("null", 2)), " tree)" , " between the different scenarios.")

@@

```{r, echo = FALSE, eval = TRUE, print = FALSE, result = 'hide'}
## Labels
labels_bc <- paste0("Full_Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

@@

```{r, warning = FALSE}
## Running the pairwise Wilcox tests:
wx_RF_best <- apply.test(whole_data, "RF", "norm", wilcox.test)
wx_Tr_best <- apply.test(whole_data, "Triples", "norm", wilcox.test)
wx_RF_null <- apply.test(whole_data, "RF", "null", wilcox.test)
wx_Tr_null <- apply.test(whole_data, "Triples", "null", wilcox.test)

@@

```{r, echo = FALSE}
## Setting the table captions
captions_wx <- paste0("Non-parametric Wilcoxon test (",rep(c("Robinson-Fould distance", "Triplets distance"), 2) ," from the ",c(rep("best", 2), rep("null", 2)), " tree)" , " between the different scenarios (p-values corrected using Bonferroni-Holm correction).")

@@

```{r, echo = FALSE, eval = TRUE, print = FALSE, result = 'hide'}
## Labels
labels_wx <- paste0("Full_Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

>>>>

```{r, echo = FALSE, warning = FALSE}
library(knitr)
## Setting the table captions
captions_pooled_scenarios <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled scenarios.")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide', warning = FALSE}
library(xtable)
make.xtable(scenarios, caption = captions_pooled_scenarios, label = "Full_Tab_pooledscenarios", path = "../Writing/Tables/")
```

@@

```{r, echo = FALSE, warning = FALSE}
kable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 3)
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide', warning = FALSE}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Full_Tab_signif", path = "../Writing/Tables/")
```

@@

```{r, warning = FALSE, warning = FALSE}
## Summarise into a table
scenario_list <- list(scenario_RF_norm, scenario_Tr_norm, scenario_RF_null, scenario_Tr_null)
comp.labels <- c("Best", rep("", 5), "Null", rep("", 5))
metric.labels <- rep(c("RF", "", "", "Tr", "", ""), 2)
test_table <- pair.test.table(scenario_list, comp.label = comp.labels, metric.label = metric.labels)
```

```{r, echo = FALSE, warning = FALSE}
## Caption
cap_pool_scen_test <- paste("Difference between the pooled scenarios. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide', warning = FALSE}
make.xtable(test_table, caption = cap_pool_scen_test, label = "Full_Tab_pooledscenarios_test", path = "../Writing/Tables/")
```

@@

```{r, warning = FALSE, warning = FALSE}
## Pooling the data per character
character_RF_norm <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "RF", best = "norm")
character_Tr_norm <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "Tr", best = "norm")
character_RF_null <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "RF", best = "rand")
character_Tr_null <- multi.pool(whole_data, param = c("c100", "c350", "c1000"),
                               metric = "Tr", best = "rand")

@@

```{r, echo = FALSE, warning = FALSE}
## Setting the table captions
captions_pooled_characters <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled number of characters.")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide', warning = FALSE}
make.xtable(characters, caption = captions_pooled_characters, label = "Full_Tab_pooledcharacters", path = "../Writing/Tables/")
```

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide', warning = FALSE}
xtable(results$validity, caption = "Normality and variance homoscedasticity tests for anova.", digit = 2, label = "Full_Tab_signif")
```

@@

```{r, echo = FALSE, warning = FALSE}
## Caption
cap_pool_char_test <- paste("Difference between the pooled number of characters. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide', warning = FALSE}
make.xtable(test_table, caption = cap_pool_char_test, label = "Full_Tab_pooledscharacters_test", path = "../Writing/Tables/")
```

@@

```{r, echo = FALSE, warning = FALSE}
## Setting the table captions
captions_pooled_taxa <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled number of taxa.")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide', warning = FALSE}
make.xtable(taxa, caption = captions_pooled_taxa, label = "Full_Tab_pooledtaxa", path = "../Writing/Tables/")
```

@@

```{r, echo = FALSE, warning = FALSE}
## Caption
cap_pool_tax_test <- paste("Difference between the pooled number of taxa. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide', warning = FALSE}
make.xtable(test_table, caption = cap_pool_tax_test, label = "Full_Tab_pooledstaxa_test", path = "../Writing/Tables/")
```

@@

```{r, echo = FALSE, warning = FALSE}
## Setting the table captions
captions_pooled_methods <- paste("Summary statistics of the normalised distances to the best or null tree for the pooled methods.")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide', warning = FALSE}
make.xtable(methods, caption = captions_pooled_methods, label = "Full_Tab_pooledmethod", path = "../Writing/Tables/")
```

@@

```{r, warning = FALSE, warning = FALSE}
## Summarise into a table
methods_list <- list(method_RF_norm, method_Tr_norm, method_RF_null, method_Tr_null)
comp.labels <- c("Best", rep("", 3), "Null", rep("", 3))
metric.labels <- rep(c("RF", "", "Tr", ""), 2)
test_table <- pair.test.table(methods_list, comp.label = comp.labels, metric.label = metric.labels)
```

```{r, echo = FALSE, warning = FALSE}
## Caption
cap_pool_met_test <- paste("Difference between the pooled methods. Bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric wilcoxon test (with Bonferonni-Holm correciton)")

@@

```{r, eval = TRUE, echo = FALSE, print = FALSE, results = 'hide', warning = FALSE}
make.xtable(test_table, caption = cap_pool_met_test, label = "Full_Tab_pooledsmethods_test", path = "../Writing/Tables/")
```

@@

```{r, warning = FALSE}
## Summarising the data
sum_RF_best <- apply.test(whole_data, "RF", "norm", NULL)
sum_Tr_best <- apply.test(whole_data, "Triples", "norm", NULL)
sum_RF_null <- apply.test(whole_data, "RF", "null", NULL)
sum_Tr_null <- apply.test(whole_data, "Triples", "null", NULL)
```

```{r, echo = FALSE, warning = FALSE}
## Setting the table captions
captions_summary <- paste("Summary statistics of the normalised", rep(c("Robinson-Fould", "Triplets"), 2), "distance to the", c(rep("best", 2), rep("null", 2)), "tree.")

@@

```{r, echo = FALSE, eval = TRUE, print = FALSE, result = 'hide', warning = FALSE}
## Labels
labels_summary <- paste0("Full_Tab_Summary", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

@@

```{r, warning = FALSE}
## Applying an lm to all the data with error
results <- test.effect.aov(whole_data,
  formula = NTS ~ scenario + (1|method) + (1|taxa) + (1|character), fun = lmer)
```

@@

```{r, warning = FALSE}
## Running the pairwise Bhattacharrya Coefficient analysis:
bc_RF_best <- apply.test(whole_data, "RF", "norm", bhatt.coeff)
bc_Tr_best <- apply.test(whole_data, "Triples", "norm", bhatt.coeff)
bc_RF_null <- apply.test(whole_data, "RF", "null", bhatt.coeff)
bc_Tr_null <- apply.test(whole_data, "Triples", "null", bhatt.coeff)
```

```{r, echo = FALSE, warning = FALSE}
## Tables
kable(bc_RF_best, row.names = FALSE, digit = 3)
kable(bc_RF_best, row.names = FALSE, digit = 3)
kable(bc_RF_best, row.names = FALSE, digit = 3)
kable(bc_RF_best, row.names = FALSE, digit = 3)
```

```{r, echo = FALSE, warning = FALSE}
## Setting the table captions
captions_bc <- paste0("Bhattacharrya Coefficient (",rep(c("Robinson-Fould distance", "Triplets distance"), 2) ," from the ",c(rep("best", 2), rep("null", 2)), " tree)" , " between the different scenarios.")

@@

```{r, echo = FALSE, eval = TRUE, print = FALSE, result = 'hide', warning = FALSE}
## Labels
labels_bc <- paste0("Full_Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))

@@

```{r, warning = FALSE, warning = FALSE}
## Running the pairwise Wilcox tests:
wx_RF_best <- apply.test(whole_data, "RF", "norm", wilcox.test)
wx_Tr_best <- apply.test(whole_data, "Triples", "norm", wilcox.test)
wx_RF_null <- apply.test(whole_data, "RF", "null", wilcox.test)
wx_Tr_null <- apply.test(whole_data, "Triples", "null", wilcox.test)

@@

```{r, echo = FALSE, warning = FALSE}
## Setting the table captions
captions_wx <- paste0("Non-parametric Wilcoxon test (",rep(c("Robinson-Fould distance", "Triplets distance"), 2) ," from the ",c(rep("best", 2), rep("null", 2)), " tree)" , " between the different scenarios (p-values corrected using Bonferroni-Holm correction).")

@@

```{r, echo = FALSE, eval = TRUE, print = FALSE, result = 'hide', warning = FALSE}
## Labels
labels_wx <- paste0("Full_Tab_BC", rep(c("RF", "Tr"), 2), c(rep("best", 2), rep("null", 2)))
